How much gut content data is required to predict trophic interactions?

### 2022-06-20 manuscript/ms_C2/ms_C2.Rmd
Incorporated most comments from Guy, Eoin and David

---
title: How much gut content data is required to predict trophic interactions?
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
geometry: margin=1in
abstract: |

  1)  Presence absence data of species interactions such as gut content data is used to parameterise food web models such as the allometric diet  breadth model (ADBM), thereby predicting interactions. Collecting and analysing these data from the field is, however, an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise food web models with high accuracy and high precision.
  2)  We apply to this problem a recently developed approach, namely Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data is used in the parameterisation. 
  3)  We estimated the minimum number of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the available gut content data.
  4)  These results suggest that one need not collect such a large quantity of gut content data to predict a food web structure using a food web model, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.

keywords:
  - gut content data
  - ADBM
  - food web accuracy
  - food web prediction
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage {amsmath}
   - \setlength\parindent{24pt}
   - \usepackage{setspace}\doublespacing
# indent: true
mainfont: Times New Roman
bibliography: bibliography.bib
biblio-style: biblatex
output:
  # word_document:
  #   fig_caption: yes
  #   number_sections: yes
  rticles::arxiv_article:
    keep_tex: true
---

\*\*AG: My comment starts with "**AG:"

# Alternate titles

-   Predicting trophic interactions using incomplete gut content data

-   Effect of the amount of gut content data on the accuracy and precision of food web prediction

@@

Each of these sources of information about trophic interactions has shortcomings. Stable isotope ratio analysis of the organism's tissue does gives indirect information of the diet of that organism via revealing approximate trophic position of that species in the food web. Although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Experimentation (e.g. feeding trials) may create unrealistic conditions where a predator is confined in a small space with a potential "prey" and is effectively "forced" into eating it (citreqd). DNA metabarcoding could have many issues such as failure to relate OTUs to species, or inability to distinguish secondary predation, i.e. the DNA signature of the prey consumed by the prey consumed by the primary item found in the predator gut. Another approach to infer missing links is literature research which involves assuming that a link will occur because another author described it in some other system, or for related predator/prey species, e.g. from the same genus or family [@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993]. This typically results in a food web that has false positives--links included when in reality no link would occur (citreqd). @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods. \*\*AG: Working on this paragraph.

Acquiring food web data from gut content analysis is time consuming and expensive (reference). In part this is due to the perception that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed. Furthermore, considerable time, resource investment, and expertise is required to process the collected samples. Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.

@@

```{r echo = FALSE, warning = FALSE}
# options(knitr.kable.NA = '')
# library(readxl)
# library(knitr)
# library(kableExtra)
# fw_table <- read_excel("../table/data_summary_fil.xlsx")
# 
# kable(fw_table, format = "latex",
#       caption = "\\label{fig:tab_1}Studies showing the type of data used to infer trophic interactions in a food web",
#       escape = FALSE) %>%
#     kable_styling(latex_options="scale_down")

```

@@

In the upcoming sections, we present the empirical food webs, the allometric diet breadth model (ADBM), and the gut content data used to infer the trophic interactions. We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC). We assessed model predictions using the true skill statistic and various structural food web properties for comparison across food webs.

@@

In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [OP: cite this https://www.go-fair.org/fair-principles/]. Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011]. A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g. species), or life stages of taxa, and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former. Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes. Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.

@@

Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web. However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010]. This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the number of gut content data [OP: this is unclear].

```{r echo=FALSE, warning=FALSE}
library(readxl)
library(knitr)
library(kableExtra)
fw_table <- read_excel("../table/fw_table.xlsx")
kable(fw_table, format = "latex",
      caption = "\\label{fig:tab_1}Information about the empirical food webs. **AG: Working on this.", escape = FALSE, align = "l") %>%
  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
  landscape(margin = "1cm") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "8em") %>%
  column_spec(7, width = "8em") %>%
  column_spec(8, width = "8em") %>%
  column_spec(9, width = "8em")

```

<!-- ### Broadstone Stream -->

[OP: I like these sections and suggest to include them for other food webs also.]

<!-- Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England. It is dominated by invertebrates as the acidity of the stream (pH 4.7-6.6) excludes fish. The stream consists of 25 common invertebrate species [@woodwardQuantificationResolutionComplex2005]. Among the predators, the three large species are *Cordulegaster boltonii* Donovan, *Sialis fuliginosa* Pict. and *Plectrocnemia conspersa* [Curtis] and the three small species are the larvae of the tanypod midges *Macropelopia nebulosa* [Meigen], *Trissopelopia longimana* [Staeger], and *Zavrelimyia barbatipes* [Kieffer]. Broadstone Stream food web is one of the most completely described food webs available for any system [@schmid-arayaImportanceMeiofaunaFood2002; @hildrewChapterSustainedResearch2009; @layerFoodWebStructure2010; and @woodwardQuantificationResolutionComplex2005a]. -->

<!-- ### Celtic Sea -->

<!-- The Celtic Sea is an area of continental shelf bordered by Ireland, the UK and the Bay of Biscay. Precise sampling locations and dates were not given in the Barnes et al. (2008) dataset, from where the data used in this chapter were extracted, so we pooled data over the whole time period and locations to capture general patterns. Only locations consistently sampled through the 1987--2001 time series were used (Blanchard et al., 2005). The feeding links of fishes in the Celtic Sea have been described in a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008): in total, 1988 feeding events from 29 predator species were included in the food web presented here. The original stomach contents data were collected from dissections carried out on board research vessels during the annual surveys carried out by the Centre for Environment, Fisheries and Aquaculture Science (Cefas) (Pinnegar et al., 2003). Predator and prey length were recorded and converted to body mass by Barnes et al. (2008) using published regression equations. Only vertebrate prey were identified and measured, with the vast majority being identified to species. -->

<!-- ### Afon Hirnant -->

<!-- The Afon Hirnant is a tributary of the Welsh Dee in North Wales, U.K. (52$^\circ$ 52'N 03$^\circ$ 34) with the study being conducted at three sites. The pH within each site ranged from about 5.5 to 7 over the course of the year. A total of 180 invertebrate samples were collected for the whole sampling periods. All individuals within the benthic samples were counted and identified to the lowest possible taxonomic level (usually species). Prey items were identified using a combination of taxonomic keys and reference slides of previously identified species, after @schmid-arayaConnectanceStreamFood2002; @schmid-arayaImportanceMeiofaunaFood2002. -->

<!-- ### Tadnoll Brook -->

<!-- Description of Tadnoll Brook here -->

<!-- ### Coilaco -->

<!-- Description of Coilaco here -->

<!-- ### Guampoe -->

<!-- Description of Guampoe here -->

<!-- ### Trancura -->

<!-- Description of Trancura here -->

@@

@@

To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @gupta2021 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic. The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled gut content data. We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

@@

-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros. [OP: I made some edits here, which I'm not sure if are correct.]

@@

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$ [OP: a short explanation would be good.]

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$  [OP: a short explanation would be good.]

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$  [OP: a short explanation would be good.]

@@

@@

We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of gut content data provided to the food web model. Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model. We also compute how well  the food web model predicts structural properties from incomplete gut content data. by computing mean standardised error in food web properties.

@@

The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). Furthermore, the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(a)). In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(c)).

@@

## Mean standardised error in structural properties with respect to the number of gut content data

Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig. \ref{fig:fig_rab}). In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.

\*\*AG: Working on this paragraph.

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."}
knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png")
```

## Dependence of the minimum gut content data on number of species, links and connectance

There was a positive trend between minimum gut content data [OP: minimum that could be used in order to ensure 95% of maximum TSS???] and number of species (S) (Fig. \ref{fig:fig_rb} (a)), links (L) (Fig. \ref{fig:fig_rb} (c)), connectance (C) (Fig. \ref{fig:fig_rb} (d)) and number of predator nodes (Fig. \ref{fig:fig_rb} (e)), with Broadstone Stream being an outlier in Fig. \ref{fig:fig_rb} (a, c, e). The minimum gut content data increases with number of gut content data sampled (Fig. \ref{fig:fig_rb} (b)). Furthermore, there seems to be a negative relationship between proportion of minimum gut (= Number of minimum gut / Number of maximum guts sampled) and number of species (S) (Fig. \ref{fig:fig_rb} (f)), links (L) (Fig. \ref{fig:fig_rb} (g)), connectance (C) (Fig. \ref{fig:fig_rb} (h)).

```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rb} (a, b, c, d, e) Number of minimum gut content data plotted against number of species (S), number of maximum guts sampled, number of links (L), connectance (C) and number of predator nodes respectively. (f, g, h) Proportion of minimum gut content data plotted against number of species (S), number of links (L) and connectance (C) respectively."}
knitr::include_graphics("../../results/misc/plot_min_gut_vs_X.png")
```

```{r echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rc} Link accumulation curve of the food web constructed using gut content data plotted against number of gut content data."}
knitr::include_graphics("../../results/misc/plot_emplinks_ngut.png")
```

@@

We have demonstrated how a food web model can be used to predict food webs reasonably well even when incomplete data about trophic interactions is available. At lower amount of gut content data, predicting with the model is better than using the data itself, while at higher amounts of gut content data, it is better to only use the data. We computed the upper limit of amount of gut content data till when it can be used to compensate for undersampling [OP: reword this sentence, it is unclear.]. This can help inform how much gut content data to actually collect when we are using a food web model to infer trophic interactions. A future development could be to make the same assessment using other food web models, and to also use food web data other than gut content data to parameterise those models.

@@

We found the minimum amount of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently, i.e. some food webs are more extensively sampled than others (Fig. \ref{fig:fig_rc}). Furthermore, it is possible that interactions in some of the food webs are are more size-structured than others, and are therefore better predicted by the ADBM and consequently require a lower number of gut content data for model parameterisation.

\*\*:AG: I would need to add information about the interactions in these food webs.

@@

When little data about trophic interactions is available, the model can be used to add data about interactions for which data is missing. Furthermore, the model predictions can be used as a guide to sample predator guts that might be significant in the food web [OP: how? I suggest to explain this in more detail.]

@@

\*\*AG: Working on this.

## Why Broadstone Stream is an outlier?

Broadstone Stream is the most sampled food web compared to all the other food webs (Fig. \ref{fig:fig_rc}), which means the observed Broadstone Stream food web might be more accurate compared to others.

\*\*AG: Working on this, not sure if this paragraph is needed.

>>>>

---
title: How much gut content data is required to predict trophic interactions?
authors:
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: anubhav.gupta@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Anubhav Gupta
  thanks: Corresponding author
- affiliation: University of Essex
  department: School of Life Sciences
  email: e.ogorman@essex.ac.uk
  location: CO4 3SQ Colchester, UK
  name: Eoin O' Gorman
- affiliation: XXX XXX
  department: XXX XXX
  email: XXX XXX
  location: XXX XXX
  name: Other authors
- affiliation: University of Zurich
  department: Department of Evolutionary Biology and Environmental Studies
  email: owen.petchey@ieu.uzh.ch
  location: 8057 Zurich, Switzerland
  name: Owen L. Petchey
geometry: margin=1in
abstract: |

  1)  One of the biggest obstacles in food web ecology is the time and effort required to adequately describe the structure of a food web using gut content data. Food web models such as the ADBM can be used to circumvent this problem by predicting the interactions based on easily measured characteristics, such as the size of organisms. However, presence-absence data such as gut content data is required to parameterise these food web models. And collecting and analysing these data from the field is an expensive and time consuming task. Therefore, it is crucial to know how much gut content data is required to parameterise food web models with high accuracy and high precision.
  2)  Here, we explore seven food webs in the literature and determine how much gut content data would be needed to accurately predict their structure using the ADBM. We use Bayesian computation to parameterise the ADBM, and true skill statistics to measure the goodness of fit, and do so while varying the amount of gut content data used in the parameterisation. 
  3)  We estimated the minimum amount of gut content data required for seven different food webs that resulted in 95% of the maximum true skill statistics achieved by the ADBM when all available gut content data was used. We found that incomplete gut content data can be used to parameterise the ADBM with the lowest amount of gut content data being 28% of the available gut content data.
  4)  These results suggest that one need not collect such a large quantity of gut content data to predict the structure of a food web, thereby reducing sampling effort considerably, while having little effect on precision or accuracy of predictions.

keywords:
  - gut content data
  - ADBM
  - food web accuracy
  - food web prediction
header-includes:
   - \usepackage{lineno}
#   - \linenumbers
   - \usepackage {amsmath}
   - \setlength\parindent{24pt}
   - \usepackage{setspace}\doublespacing
# indent: true
mainfont: Times New Roman
bibliography: bibliography.bib
biblio-style: biblatex
output:
  # word_document:
  #   fig_caption: yes
  #   number_sections: yes
  rticles::arxiv_article:
    keep_tex: true
---

@@

Each of these sources of information about trophic interactions has shortcomings. For example: Stable isotope ratio analysis of the organism's tissue does not give direct information of the diet of that organism but rather gives approximate trophic position of that species in the food web [@wadaUseStableIsotopes1991; @jenningsTrophicLevelsMarine2015]. Although mixing models can be used to determine what prey items are most likely fed upon by a predator, this results in uncertainty in the estimates [@kadoyaIsoWebBayesianIsotope2012; @crawfordApplicationsStableIsotope2008]. Similarly, DNA metabarcoding could have issues in detecting secondary predation or cannibalism [@pompanonWhoEatingWhat2012; @nielsen2018] and is prone to environmental contamination (e.g. DNA in the water swallowed along with DNA from an aquatic consumer's prey cannot be differentiated from actual prey) [@kellyUsingEnvironmentalDNA2014]. Furthermore, construction of food webs via literature review can lead to false positives--links included when in reality no link would occur because it makes an assumption that the species interactions inferred from a system will occur in another system as well[@grayJoiningDotsAutomated2015; @cohen2014; @goldwasser1993].

 @nielsen2018 have shown that gut content analysis method has a better match with real diet when compared to other methods.

Acquiring food web data from gut content analysis is time consuming and expensive (AG: Do we need a reference? Next sentence explains the reason.). In part this is due to the perception that many gut contents must be collected and analysed in order to be confident that the majority of possible trophic links among species have been observed. Furthermore, considerable time, resource investment, and expertise is required to process the collected samples. Hence, there is of considerable importance to know the minimum number of gut contents and of which consumer species that are required to parameterise a food web model with high accuracy and high precision, so that one knows when is a good time to stop collecting any further empirical data on the food web.

@@

@@

In the upcoming sections, we present the empirical food webs, the allometric diet breadth model (ADBM), and the gut content data used to infer the trophic interactions. We also give a detailed account of using partial gut content data to parameterise the ADBM using rejection approximate Bayesian computation (ABC). We assessed model predictions using the true skill statistic for comparison across food webs.

@@

In our study, we used food webs for which gut content data is available at an individual level and data that is or that we could make FAIR [@wilkinsonFAIRGuidingPrinciples2016]. Presence and absence interactions of food web data can be aggregated in different ways [@gilljamSeeingDouble2011]. A common way of aggregating food web data is the taxonomic approach, in which nodes in the food web are taxa (e.g. species), or life stages of taxa, and one species is said to feed on another species if at least one individual of the latter is found in at least one gut of the former. Another approach is based on size, rather than taxonomy, and in this the nodes in the food web are size classes. Here, a feeding link occurs between two size classes if at least one prey item within a size class was found in the gut of another size class, irrespective of their taxonomy.

@@

Our study is based on the assumption that the food web constructed using the complete gut content data is the true food web. However, this might not be the case because the links are still under-sampled for many nodes [@woodwardIndividualBasedFoodWebs2010]. This could result in a lower true skill statistic (TSS) of the predicted food web from the ADBM, which can result in a biased estimate of the minimum number of gut content data required to achieve 95% of the TSS achieved using complete gut content data.

In the following sections 2.1.1-2.1.5, we briefly explain seven empirical food webs used in our study. The text used in those sections are paraphrased from @gilljamSeeingDouble2011.

<!-- ```{r echo=FALSE, warning=FALSE} -->

<!-- library(readxl) -->

<!-- library(knitr) -->

<!-- library(kableExtra) -->

<!-- fw_table <- read_excel("../table/fw_table.xlsx") -->

<!-- kable(fw_table, format = "latex", -->

<!--       caption = "\\label{fig:tab_1}Information about the empirical food webs. AG: Working on this.", escape = FALSE, align = "l") %>% -->

<!--   kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>% -->

<!--   landscape(margin = "1cm") %>% -->

<!--   column_spec(1, width = "3cm") %>% -->

<!--   column_spec(2, width = "8em") %>% -->

<!--   column_spec(7, width = "8em") %>% -->

<!--   column_spec(8, width = "8em") %>% -->

<!--   column_spec(9, width = "8em") -->

### Broadstone Stream

Broadstone Stream (51$^\circ$ 05' N 0$^\circ$ 03' E; 120 m above sea-level) is a second-order tributary of the River Medway in south-east England. At the time of sampling in 1996--1997, the stream was acidic (pH 4.7--6.6) and fishless. About 31 common species make up the macroinvertebrate food web, including six major predators and detritivores like stoneflies and chironomids [@woodwardQuantificationResolutionComplex2005].

Between June 1996 and April 1997, thirty randomly scattered benthic Surber sample-units (25cm $\times$ 25cm quadrat; mesh aperture 330mm) were taken every two months and kept in 5% formalin. All individuals retrieved from the benthos and identified in stomach contents had their linear body dimensions quantified and converted to dry mass using known regression formulae (listed in @woodwardBodysizeDeterminantsNiche2002).

The predators' foreguts were dissected and analysed with 400 magnification in the Surber samples. The individual body masses of eaten prey were calculated using the same methods as for the benthic samples, using reference slides as a guide [@woodwardQuantificationResolutionComplex2005]. Over the six sample instances, a single dataset was produced. Each predator and prey individual involved in a feeding relationship was measured and converted into their respective body masses, resulting in a total of 2893 individuals.

### Celtic Sea

The Celtic Sea is a continental shelf area that is bounded by Ireland, the United Kingdom, and the Bay of Biscay. Because the @barnesPredatorPreyBody2008 dataset, from which the data utilised in this chapter were taken, did not provide precise sampling sites and dates, the data was pooled throughout the whole time period and locations to capture broad tendencies. Only places that were sampled consistently from 1987 to 2001 were used [@blanchardClimateFishingInfluence2005].

In a published global dataset of individual predator and prey body sizes and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the Celtic Sea were described. The original stomach contents data were acquired during annual surveys conducted by the Centre for Environment, Fisheries, and Aquaculture Science (Cefas) on board research vessels during dissections [@pinnegarDoesDietCeltic2003]. @barnesPredatorPreyBody2008 used known regression equations to measure predator and prey lengths and convert them to body mass.

### Afon Hirnant

Three sites in the Afon Hirnant, in North Wales, UK ($52^\circ$ 52' N $03^\circ$ 34' W), were used for the study. The average yearly discharge was 2.08 to 7.26 $m^3/s$, with a pH ranging from 5.5 to 7. (check @figueroaFoodWebDynamics2007 and @woodwardChapterIndividualBasedFood2010 for full details). Invertebrates were collected using a Hess sampler (sampling area: 0.028 $m^2$; mesh aperture 80 $\mu m$), with 15 sample-units obtained at random at each site and season, totaling 180 samples across the sampling period. The invertebrate fauna was promptly preserved in 100% ethanol and sorted in the lab. By removing predators' foreguts, which were mounted in Euparal media and viewed at 400 magnification, feeding interactions were determined.

Every predator's linear dimensions (for example, body length) and individual prey items inside each predator's foregut were measured and then translated to body mass values using published regression equations for each taxon (presented in @woodwardChapterIndividualBasedFood2010). If the prey items were highly digested, the average body length of individuals in the same family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was used. The body lengths of Chironomidae (Diptera) were calculated using previously established species-specific regressions between head capsule width and body length [@figueroaFoodWebDynamics2007].

### Tadnoll Brook

The Tadnoll Brook is a tributary of the River Frome in Southern England, UK, with a mean annual discharge of 0.35 $m^3/s$ and a pH of 6.9--7.7. (Edwards et al., 2009b).

A 240-m reach was sampled every two months between February and December 2005 to create the summary food web. A Surber sampler was used to collect invertebrates every two months (0.06 m2; mesh aperture 300 mm). 20 random samples were taken on each occasion, stored in the field in 4% (w/v) formalin, and then sorted for invertebrates. Fish were captured with an electrofisher, anaesthetized with 2-phenoxyethanol, recognised to species, measured, and weighed on each occasion (Woodward et al., 2010). The guts of trout (Salmo trutta L.) with fork lengths more than 70 mm were then flushed with a tiny manual water pump and stored in 4% formalin. For smaller trout and other fish species (*Cottus gobio*, *Anguilla anguilla*, *Phoxinus phoxinus*, *Barbatula barbatula*, *Gasterosteus aculeatus*), specimens were sacrificed and frozen for subsequent dissection.

Gut contents analysis was performed on each sample occasion for the fish assemblage, whereas invertebrates had far less varied diets and were only characterised in May and October. Individuals of the benthos' numerically dominant or trophically important invertebrate taxa were taken from the Surber samples, dissected, and the contents of the foregut investigated for animal prey, which were recognised at $400\times$ magnification by comparison with reference specimens. The taxa used to examine stomach contents covered more than 95% of the individuals observed in the Benthos. Wherever possible, predators' gut contents were matched to species, and linear body dimensions were measured. Using established regression equations, the dry mass of prey items and invertebrate predators was calculated [@benkeLengthMassRelationshipsFreshwater1999; @ganiharBiomassEstimatesTerrestrial1997; @burgherrRegressionAnalysisLinear1997; @gonzalezSizemassRelationshipsStream; @smockRelationshipsBodySize1980; @edwardsRelationshipLengthMass2009; @meyerRelationshipBodyLength1989].

### Guampoe, Coilaco and Trancura Rivers, Chile

Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the catchment area of the Tolten River in south Chile, South America, were studied in a similar way. The Coilaco River (discharge 2.1--16.8 $m^3/s$), Guampoe River (output 1.8--7.5 $m^3/s$), and Trancura River (discharge 8.8--49.3 $m^3/s$) are all pH 6.7--7.6 circumneutral rivers [@figueroaFoodWebDynamics2007].

In each river, eight benthic samples were taken in each season between 1984 and 1985, totaling 96 sample-units for the whole sampling period (Campos et al., 1985). Invertebrates were gathered using a Surber sampler (sampling area: 0.09 $m^2$; mesh aperture 250 $\mu m$) and stored in 70% ethanol before being transported to the lab for species identification and food web analysis.

The feeding linkages were discovered by analysing the gut contents of all individuals observed in each sample. Large invertebrates had their guts removed and mounted in Euparal, whilst small specimens were mounted whole and studied with $400\times$ magnification. Following Schmid (1993) and [@schmid-arayaConnectanceStreamFood2002], species prey items detected on each gut were identified using previously mounted reference slides. Using known regression equations (mentioned in @reissExistingPlentyAbundance2008; @baumgartnerPredictiveLengthDry2003; @miserendinoRelacionesLongitudpesoPara2001; @woodwardIndividualBasedFoodWebs2010), all linear dimensions were translated to body mass estimates.

@@

**Comment AG: Is it necessary to have the sections 1.1 and 1.2 of the supplementary information in the Supplementary information or shall the sections 1.1 and 1.2 be migrated to the main text (manuscript)?**

@@

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data. Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\\% of the maximum TSS. (b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only. The dashed line shows where the ratio is one for reference."}
knitr::include_graphics("../../manuscript/fig/ms_C2(1).png")
```

To fit the ADBM to a gut content dataset (be it complete or partial), we used the rejection ABC method we previously developed in @guptaSimultaneouslyEstimatingFood2022 to accept a parameter value from a prior distribution which would have resulted in the minimum distance, where distance = 1 - True skill statistic. The true skill statistic was computed between the diets predicted from the ADBM, and those observed in the sampled gut content data. We repeated this process $n~(= 100)$ times for every $i$ number of guts, where $i$ lies between 1 and total number of gut content data in the pool.

@@

-   A pool of gut content data $G: G = \{g_1, g_2, \dots, g_n\}$, where $g_{n}$ is the observed diet matrix containing ones and zeros.

@@

-   A summary statistic $s(x): s(x) \subseteq model(\theta)$, where $s(x)$ is the diet of some or all of the predators.

-   A distance function $d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)$, which quantifies how close the observed diet is to the predicted diet of some or all of the predators.

-   An observed food web $Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}$, where $d_{p_k}'$ is the observed diet matrix of predator $k$ containing ones and zeros.

@@

## Computing the minimum gut content data

Using TSS of the predicted food webs for different number of predator guts, we computed the number of gut content data that results in the mean TSS equal to the 95% of the mean TSS achieved by the model using all the predator guts for a food web. We call this number of gut content data as the minimum gut content data.

@@

We first present how the accuracy of the food web model in predicting trophic interactions varies with increasing amount of gut content data provided to the food web model. Then, we calculate the number of gut content data for each food webs that results in accuracy equal to 95% of the maximum true skill statistics predicted by the food web model.

@@

The true skill statistics of the food webs predicted by the ADBM using subsets of gut content data improved quickly for lower number of predator guts (Fig. \ref{fig:fig_ra}) (a, c, e, g, i, k, m). Furthermore, the width of the prediction interval of the true skill statistics decreased with increasing number of predator guts with the mean TSS asymptoting to the maximum mean TSS achieved by the ADBM when all the gut content data was used. Although the maximum TSS varied among the food webs, the qualitative increase in the TSS was the same.

For Broadstone Stream food web, with only 381 gut contents, which is 38% of the total gut content data, the ADBM predicted the food web with the mean TSS of 0.74 which was 95% of the mean TSS (0.78) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(a)). In case of the Celtic Sea food web, only 171 gut content data which is 35% of the total gut content data was required by the ADBM to predict food web with TSS equal to 95% of the mean TSS (0.68) achieved using complete gut content data (Fig. \ref{fig:fig_ra}(c)).

@@

<!-- ## Mean standardised error in structural properties with respect to the number of gut content data -->

<!-- Mean standardised error in structural properties of Afon Hirnant, Broadstone Stream, Celtic Sea and Tadnoll Brook food web reduced drastically with increasing number of predator gut content data at low number of predator gut content data (Fig. \ref{fig:fig_rab}). In case of Broadstone Stream food web, the 95% prediction interval reduced as well with increasing number of predator gut content data.  -->

<!-- \*\*AG: Working on this paragraph. -->

<!-- ```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_rab} Mean standardised error in structural properties of different food webs with respect to the number of gut content data."} -->

<!-- knitr::include_graphics("../../results/misc/plot_mse_ngut_all.png") -->

## Dependence of the minimum gut content data on number of links and connectance

There was a significant positive relationship between the minimum number of gut content data (i.e the amount of gut content data used in order to ensure 95% of the maximum TSS) and the connectance of the food webs (Fig. \ref{fig:fig_rb} (a)). Similarly, we also observed a positive relationship between the minimum number of gut content data and the number of trophic links (L) in the food webs, however this relationship was not significant (Fig. \ref{fig:fig_rb} (b)). Furthermore, there was a significant positive relationship between the number of minimum gut content data and the the number of maximum gut content data sampled (Fig. \ref{fig:fig_rb} (c)) for food webs.

```{r echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_rb} (a, b, c) Number of minimum gut content data (i.e the amount of gut content data used in order to ensure 95\\% of the maximum TSS) plotted against number of links (L), connectance (C) and number of maximum guts sampled respectively. Solid lines are linear regression ((a) t = 3.138, df = 5, P = 0.0257; (b) t = 0.876, df = 5, P = 0.421; (c) t = 9.571, df = 5, P = 0.0002) and grey region represents 95\\% confidence intervals."}
knitr::include_graphics("../../results/misc/plot_min_gut_vs_X.png")
```

@@

We have demonstrated how a food web model can be used to predict food webs reasonably well even when incomplete data about trophic interactions is available. At lower amount of gut content data, predicting with the model is better than using the data itself, while at higher amounts of gut content data, it is better to only use the data. This can help inform how much gut content data to actually collect when we are using a food web model to infer trophic interactions. A future development could be to make the same assessment using other food web models, and to also use food web data other than gut content data to parameterise those models.

@@

We found the minimum amount of gut content data to vary across food webs and this could be due to the possibility that the food webs are sampled differently, i.e. some food webs are more extensively sampled than others (SI Fig. S2). Furthermore, it is possible that interactions in some of the food webs are are more size-structured than others, and are therefore better predicted by the ADBM and consequently require a lower number of gut content data for model parameterisation.

@@

When little data about trophic interactions is available, the model can be used to add data about interactions for which data is missing. Furthermore, the model predictions can be used as a guide to sample those predator guts for which we do not have enough information on the presence of interactions from the empirical gut content samples but the model suggests there are interactions. Therefore, with enough number of predator guts sampled one might possibly observe those missed interactions.

<!-- [OP: how? I suggest to explain this in more detail.] -->

@@

In all the food webs, the ratio TSS(Model)/TSS(Data) decreased with increasing number of predator guts (Fig. \ref{fig:fig_ra} (b, d, f, h, j, l, n)). This suggests when less data is available it is better to use the model and when more data is available it is better to only use the data to predict trophic interactions. At lower number of predator guts the model fills up the missing interactions that were not observed in the gut content data, therefore resulting in model performing better as compared to data alone. Wile at higher number of predator guts the model is probably predicting some presence or absence of links i.e. false positives and false negatives resulting in a lower TSS as compared to that of data alone.

<!-- ## Why Broadstone Stream is an outlier? -->
